Methods Power Study - Middle Simulations

### 2023-08-30 simulation_study/simulate_summary_middle.Rmd
simulations done!

---
title: "Methods Power Study - Ceiling Simulations"
author: "Erin M. Buchanan"
date: "Last Knitted: `r Sys.Date()`"
output: html_document
---

@@

```{r}
set.seed(548902) # 233232
library(dplyr)
library(ggplot2)
library(tidyr)
library(broom)
library(papaja)
library(rio)
```

@@

  # small potential variability overall, sort of 1-7ish scale
  mu.small <- rnorm(30, 6, .25)
  sigma.small.s <- rnorm(30, 2, .2)
  sigma.small.m <- rnorm(30, 2, .4)
  sigma.small.l <- rnorm(30, 2, .8)

@@

  # medium potential variability 0 to 100 scale
  mu.medium <- rnorm(30, 85, 10)
  sigma.medium.s <- rnorm(30, 25, 4)
  sigma.medium.m <- rnorm(30, 25, 8)
  sigma.medium.l <- rnorm(30, 25, 16)

@@

  # large potential variability in the 1000s scale
  mu.large <- rnorm(30, 2500, 150)
  sigma.large.s <- rnorm(30, 400, 50)
  sigma.large.m <- rnorm(30, 400, 100)
  sigma.large.l <- rnorm(30, 400, 200)

@@

- Within that function, create the scale size variable: 
  - Small scale data 1-7, mean 6, sd of mean .25
  - Medium scale data 0-100, mean 85, sd of mean 10
  - Large scale data no range, mean 2500, sd of mean 150
  - These choices are meant to mimic popular scale choices that have skewed effects 
- Additionally, create the scale heterogeneity variable:
  - Small scale heterogeneity, sd 2, sd of sd .2 .4 .8
  - Medium scale heterogeneity, sd 25, sd of sd 4, 8, 16
  - Large scale heterogeneity, sd 400, sd of sd 50, 100, 200

@@

```{r eval = F}
all_sim <- bind_rows(readRDS("simulation_study/simulation_ceiling/simulation_2023-08-30_rstudio_ceiling.Rdata"),
                     bind_rows(readRDS("simulation_study/simulation_ceiling/simulation_2023-08-30_windows_ceiling.Rdata")),
                     bind_rows(readRDS("simulation_study/simulation_ceiling/simulation_2023-08-30_server_ceiling.Rdata"))) %>% unique()

@@

```{r}
export(summary_long, "simulation_study/simulation_ceiling/simulated_summary_data_ceiling.csv", row.names = F)
```

>>>>

---
title: "Methods Power Study - Middle Simulations"
author: "Erin M. Buchanan"
date: "Last Knitted: `r Sys.Date()`"
output: html_document
---

@@

```{r}
set.seed(895893) # 233232
library(dplyr)
library(ggplot2)
library(tidyr)
library(broom)
library(papaja)
library(rio)
```

@@

  # small potential variability overall, sort of 1-7ish scale
  mu.small <- rnorm(30, 4, .25)
  sigma.small.s <- rnorm(30, 2, .2)
  sigma.small.m <- rnorm(30, 2, .4)
  sigma.small.l <- rnorm(30, 2, .8)

@@

  # medium potential variability 0 to 100 scale
  mu.medium <- rnorm(30, 50, 10)
  sigma.medium.s <- rnorm(30, 25, 4)
  sigma.medium.m <- rnorm(30, 25, 8)
  sigma.medium.l <- rnorm(30, 25, 16)

@@

  # large potential variability in the 1000s scale
  mu.large <- rnorm(30, 1000, 150)
  sigma.large.s <- rnorm(30, 400, 50)
  sigma.large.m <- rnorm(30, 400, 100)
  sigma.large.l <- rnorm(30, 400, 200)

@@

- Within that function, create the scale size variable: 
  - Small scale data 1-7, mean 4, sd of mean .25
  - Medium scale data 0-100, mean 50, sd of mean 10
  - Large scale data no range, mean 1000, sd of mean 150
  - These choices are meant to mimic popular scale choices 
- Additionally, create the scale heterogeneity variable:
  - Small scale heterogeneity, sd 2, sd of sd .2 .4 .8
  - Medium scale heterogeneity, sd 25, sd of sd 4, 8, 16
  - Large scale heterogeneity, sd 400, sd of sd 50, 100, 200

@@

```{r eval = F}
all_sim <- bind_rows(readRDS("simulation_study/simulation_middle/simulation_2023-08-29_mac_middle.Rdata")) %>% unique()

@@

```{r}
export(summary_long, "simulation_study/simulation_middle/simulated_summary_data_middle.csv", row.names = F)
```
